hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-06-17 inst/manuscript/paper.Rmd
rerender with updated apa.csl

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=TRUE}
WI_hatch$days_to_develop; WI_hatch$dev.period
```

@@

`WI_hatch$dev.period` -- A 1x2 dataframe containing the spawning date (as input via `predict_phenology(spawn.date = ...)`) and predicted development completion date.

@@

all_res$start <- c(
  catfish_res$dev.period$start,
  smb_res$dev.period$start,
  sturgeon_res$dev.period$start
)

all_res$stop <- c(
  catfish_res$dev.period$stop,
  smb_res$dev.period$stop,
  sturgeon_res$dev.period$stop
)

@@

# fish emerge May 1, before June 1
bt_emergence$dev.period$stop
```

@@

```{r, echo=TRUE}
# apply predict_phenology() over multiple sites and spawn dates
hatch_res <- isaak_summ_bt |>
  mutate(
    dev_period = map2(
      summ_obj,                  # summarized temperature data object
      spawn_dates,               # list of spawn dates
      predict_phenology,         # function to apply
      temperature = daily_temp,  # column of temperature data in `summ_obj`
      dates = date,              # column of date in `summ_obj`
      model = bt_hatch           # model to use (from model_select())
    ) |>
      map_df("dev.period") |>    # pull out just dev.period results
      list()
  ) |>
  select(site, dev_period) |>           # just select the columns we want
  unnest(cols = c(dev_period)) |>       # un-nest everything
  mutate(days_to_hatch = stop - start)  # make a new column of days to hatch
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```

@@

```{r, echo=TRUE}
WI_hatch$days_to_develop; WI_hatch$dev_period
```

@@

`WI_hatch$dev_period` -- A 1x2 dataframe containing the spawning date (as input via `predict_phenology(spawn.date = ...)`) and predicted development completion date.

@@

all_res$start <- c(
  catfish_res$dev_period$start,
  smb_res$dev_period$start,
  sturgeon_res$dev_period$start
)

all_res$stop <- c(
  catfish_res$dev_period$stop,
  smb_res$dev_period$stop,
  sturgeon_res$dev_period$stop
)

@@

# fish emerge May 1, before June 1
bt_emergence$dev_period$stop
```

@@

```{r, echo=TRUE}
# apply predict_phenology() over multiple sites and spawn dates
hatch_res <- isaak_summ_bt |>
  mutate(
    dev_period = map2(
      summ_obj,                  # summarized temperature data object
      spawn_dates,               # list of spawn dates
      predict_phenology,         # function to apply
      temperature = daily_temp,  # column of temperature data in `summ_obj`
      dates = date,              # column of date in `summ_obj`
      model = bt_hatch           # model to use (from model_select())
    ) |>
      map_df("dev_period") |>    # pull out just dev_period results
      list()
  ) |>
  select(site, dev_period) |>           # just select the columns we want
  unnest(cols = c(dev_period)) |>       # un-nest everything
  mutate(days_to_hatch = stop - start)  # make a new column of days to hatch
```
